\documentclass[handout, svgnames, aspectratio = 1610]{beamer}

\usepackage{microtype, siunitx, shortvrb}
\MakeShortVerb\"
\providecommand \pkg {\textsf}
\providecommand \cls {\textsf}
\usepackage[mono = false]{libertine}
\usetheme[logo   = westlake-logo.pdf,  badge  = westlake-badge.pdf,
          mainbg = westlake-paint.png, basebg = plain.png]{westlake}
\graphicspath{{./media/}}
\usepackage[superscript]{cite}
\makeatletter \renewcommand \@citess [1]{\textsuperscript{[#1]}} \makeatother
\DeclareRobustCommand \meta[1]
  {\itshape \ensuremath \langle #1\/\ensuremath \rangle \upshape}
\ExplSyntaxOn
\DeclareDocumentCommand \key { s m }
  {
    \IfBooleanTF {#1} { \textcolor{red}{\ttfamily \bfseries #2} }
      {
        \group_begin: \ttfamily
        \seq_set_from_clist:Nn \l_tmpa_seq {#2}
        \seq_set_map:NNn \l_tmpb_seq \l_tmpa_seq
          { \exp_not:n { \textcolor{red}{\bfseries ##1} } }
        \seq_use:Nn \l_tmpb_seq { ,~ } \:=\:
        \group_end:
      }
  }
\DeclareCommandCopy \val \meta
\ExplSyntaxOff

\title[beamerthemeWestlake]{Westlake Beamer Theme}
\author[Mingyu Xia]{Mingyu Xia \texttt{<%
  \href{mailto:xiamingyu@westlake.edu.cn}{xiamingyu@westlake.edu.cn}>}}
\makeatletter
\date{\texorpdfstring
  {\texttt{Released \westlake@date}}{Released \westlake@date}}
\makeatother

\begin{document}

\maketitle

\section{INTRODUCTION}

\begin{frame}{Theme Introduction}
  This is the Westlake Beamer Theme.
  Different from the basic \cls{beamer} class,
  this theme provides
  \begin{alertblock}{Highlights}
    \begin{itemize}
      \item Decorations at the bottom of the homepage;
      \item Progress bar with percentage at the north east corner of
      every slide and section pages;
      \item Interfaces for modifying the logo, backgrounds, etc.
    \end{itemize}
  \end{alertblock}
  {\usebeamerfont{frametitle}\usebeamercolor[fg]{frametitle}
    The meaning of Westlake}
  \begin{exampleblock}{A freshwater lake}
    West Lake, also known as Xihu and by other names,
    is a freshwater lake in Hangzhou, China.
    Situated to the west of Hangzhou's former walled city,
    the lake has a surface area of \qty{6.39}{\km^2} (\qty{2.47}{mi^2}),\cite{1}
    stretching \qty{3.2}\km (\qty{2.0}{mi}) from north to south
    and \qty{2.8}\km (\qty{1.7}{mi}) from east to west.\cite{2}
  \end{exampleblock}
  \begin{block}{A private research university}
    Westlake University is a private research university in
    Hangzhou, Zhejiang, China.
  \end{block}
\end{frame}

\section{USAGE}

\begin{frame}[t, fragile]{User Interface}
  To load this package, under the \pkg{beamer} class, write the line\par
  \begin{quote}
    "\usetheme["\meta{keys}"]{Westlake}"
  \end{quote}\par
  where the supported keys are
  \begin{itemize}
    \item \key{themergb}\val{fp num, fp num, fp num} to config the rgb values
    (ranges between $0$ to $1$) of the theme color
    (Default: "0.132, 0.324, 0.570").
    \item \key{logo, badge, mainbg, basebg}\val{file} to config the graphic
    files for
    \begin{itemize}
      \item logo: appears at the right side of every slide,
      \item badge: appears at the north west corner of homepage
      and section pages,
      \item main background: appears on homepage and section pages, and
      \item base background: appears on other pages, respectively.
    \end{itemize}
  \end{itemize}
  {\usebeamerfont{frametitle}\usebeamercolor[fg]{frametitle} Reference}
  \begin{thebibliography}{9}
    \bibitem{1}
    Zhejiang Provincial Bureau of Surveying and Mapping. 2010-09-30.
    \bibitem{2}
    Overview of the West Lake. Hangzhou Chronicles (in Chinese).
    \newblock
    Zhonghua Book Company. 1995. ISBN 7101017193.
  \end{thebibliography}
\end{frame}

\section{Thanks for Listening! Any Questions?}

\end{document}
